landlord

### 2022-10-27 src/landlord.Rmd
through line 84 dilter rent control

```{r}
#PICK UP HERE!
#calculate landlord category score

#input landlord weights for each indicator in the following order: rent control, security deposit limit, notice for entry, eviction notice days
#Get weights from Owen
#Weights must sum to 1
landlord_weights <- c(0.25, 0.25, 0.25, 0.25)

#make landlord_score column
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    landlord_score = MSA #this is just a place holder
  )
size <- dim(MSA_landlord_data)
for (i in 1:size[1]) {
  MSA_x_data <- c(MSA_landlord_data$rent_control_binary[i], 
                  MSA_landlord_data$security_depopsit_limit_binary[i],
                  MSA_landlord_data$notice_for_entry_days_binary[i],
                  MSA_landlord_data$eviction_notice_days_normalized_inverted[i])
  MSA_landlord_data$landlord_score[i] = weighted.mean(MSA_x_data, landlord_weights)
}
```

```{r}
#test Virginia new laptop on github
#testing github token setupf
```

>>>>

```{r}
#calculate landlord category score

#input landlord weights for each indicator in the following order: eviction notice days, security deposit limit, notice for entry

#Weights must sum to 1
landlord_weights <- c(0.9, 0.05, 0.05)

#make landlord_score column
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    landlord_score = MSA #this is just a place holder
  )
size <- dim(MSA_landlord_data)
for (i in 1:size[1]) {
  MSA_x_data <- c(MSA_landlord_data$eviction_notice_days_normalized_inverted[i],
                  MSA_landlord_data$security_depopsit_limit_num[i],
                  MSA_landlord_data$notice_for_entry_days_num[i]
                  )
  MSA_landlord_data$landlord_score[i] = weighted.mean(MSA_x_data, landlord_weights)
}
```

```{r}
#PICK UP HERE
#If there is rent control, immediately disqualify location 
```
